---
title: "Lab 1 - ID"
author: "Ilayda Dinc"
date: "1/9/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(janitor)
library(kableExtra)
```

Read in noaa_fisheries.csv data

it needs to look into the data folder-- use data/ -- not really useful
using here packages gives a way to get away with it. give the pathway using commas.

```{r}
us_landings <- read_csv(here("data", "noaa_fisheries.csv"))
```

titles need to be changed
dollar sign - r will read it as character
mutate can be useful to reformat an existing column -- usually you don't wanna replace an existing column but here is fine
check the class of dollars_usd - it is probably gonna be character. We could use tidyr separate.We can use readr to parse data. parse_number will drop any non-numeric characters before or after the first number.

Now, make a tidy version of the data frame

```{r}
landings_tidy<-us_landings %>% 
  janitor::clean_names() %>% 
  mutate(state= str_to_lower(state),
        afs_name=str_to_lower(afs_name)) %>% 
  mutate(dollars_num=parse_number(dollars_usd))
  
```

Let's just get some information for salmon:

```{r}
salmon_landings <-landings_tidy %>% 
  mutate(afs_clean=str_remove(afs_name,pattern="aggregate"))
  
```

word aggreagate is not relevant.
